---
title: "DSCUNIDataSets: A Comprehensive Collection of University and Engineering Datasets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DSCUNIDataSets: A Comprehensive Collection of University and Engineering Datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(DSCUNIDataSets)
library(ggplot2)
library(dplyr)
```

# Introduction

The `DSCUNIDataSets` package provides a curated collection of datasets designed to support research and analysis in various domains of engineering, clustering, and ordered regression studies. The package includes datasets such as mechIng_df, which contains mechanical engineering data used to illustrate ordered isotonic regression, and bolts_df, which contains data from experiments analyzing the effects of machine adjustments on the time to count bolts.

This package is intended for researchers, analysts, and practitioners who require ready-to-use, high-quality datasets for methodological exploration, statistical modeling, and applied research. All datasets are maintained in their original form, ensuring data integrity, and are compatible with standard R workflows.

## DSC UNI Plot

```{r DSC-plot, message=FALSE, warning=FALSE, fig.width=7, fig.height=5}

# Manually transform the data to long format using only dplyr
mechIng_long <- bind_rows(
  mechIng_df %>% select(x, value = g1) %>% mutate(group = "g1"),
  mechIng_df %>% select(x, value = g2) %>% mutate(group = "g2")
)

# Line plot comparing g1 and g2 as a function of x
ggplot(mechIng_long, aes(x = x, y = value, color = group)) +
  geom_line(size = 1) +
  labs(
    title = "Comparison of g1 and g2 as a Function of x",
    x = "x (input variable)",
    y = "Value",
    color = "Group"
  ) +
  theme_minimal() +
  theme(
    text = element_text(size = 12),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )

```

## Conclusion

The `DSCUNIDataSets` package provides a unified interface for accessing a wide range of curated datasets from diverse domains. Covering various topics and formats, the package includes clean, preloaded datasets that are ready for immediate use in R, enabling researchers, analysts, and data enthusiasts to explore, analyze, and visualize data efficiently.

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>
